\section{Internal Gains}\label{internal-gains}

A number of internal variables describe design levels for the various types of internal gains.

\subsection{People Count Design Level}\label{people-count-design-level}

The internal variable ``People Count Design Level'' provides information about the maximum number of people associated with each people input object. The units are number of people. This is the value entered in, or resulting from intermediate calculations using, the inputs in the People object. This variable is useful for scaling the values assigned to the ``Number of People'' control in the ``People'' EMS actuator.

\subsection{Lighting Power Design Level}\label{lighting-power-design-level}

The internal variable ``Lighting Power Design Level'' provides information about the maximum lighting electrical power level associated with each Lights input object. The units are Watts. This is the value entered in, or resulting from intermediate calculations using, the inputs in the lights object. This variable is useful for scaling the values assigned to the ``Electricity Rate'' control in the ``Lights'' EMS actuator.

\subsection{Plug and Process Power Design Level}\label{plug-and-process-power-design-level}

The internal variable ``Plug and Process Power Design Level'' provides information about the maximum electrical equipment power level associated with each ElectricEquipment input object. The units are Watts. This is the value entered in, or resulting from intermediate calculations using, the inputs in the ElectricEquipment object. This variable is useful for scaling the values assigned to the ``Electricity Rate'' control in the ``ElectricEquipment'' EMS actuator.

\subsection{Gas Process Power Design Level}\label{gas-process-power-design-level}

The internal variable ``Gas Process Power Design Level'' provides information about the maximum gas equipment power level associated with each GasEquipment input object. The units are Watts. This is the value entered in, or resulting from intermediate calculations using, the inputs in the GasEquipment object. This variable is useful for scaling the values assigned to the ``Gas Power Level'' control in the ``GasEquipment'' EMS actuator.

\subsection{Process District Heat Design Level}\label{process-district-heat-design-level}

The internal variable ``Process District Heat Design Level'' provides information about the maximum district heating power level associated with each HotWaterEquipment input object. The units are Watts. This is the value entered in, or resulting from intermediate calculations using, the inputs in the HotWaterEquipment object. This variable is useful for scaling the values assigned to the ``District Heating Power Level'' control in the ``HotWaterEquipment'' EMS actuator.

\subsection{Process Steam District Heat Design Level}\label{process-steam-district-heat-design-level}

The internal variable ``Process Steam District Heat Design Level'' provides information about the maximum district heating power level associated with each SteamEquipment input object. The units are Watts. This is the value entered in, or resulting from intermediate calculations using, the inputs in the SteamEquipment object. This variable is useful for scaling the values assigned to the ``District Heating Power Level'' control in the ``SteamEquipment'' EMS actuator.

\subsection{Other Equipment Design Level}\label{other-equipment-design-level}

The internal variable ``Other Equipment Design Level'' provides information about the maximum power level associated with each OtherEquipment input object. The units are Watts. This is the value entered in, or resulting from intermediate calculations using, the inputs in the OtherEquipment object. This variable is useful for scaling the values assigned to the ``Power Level'' control in the ``OtherEquipment'' EMS actuator.

\subsection{Simple Zone Baseboard Capacity}\label{simple-zone-baseboard-capacity}

The internal variables called ``Simple Zone Baseboard Capacity At Low Temperature'' and ``Simple Zone Baseboard Capacity At High Temperature'' provide information about the power levels associated with each ZoneBaseboard:OutdoorTemperatureControlled object. These value are inputs to that object. The variables are useful for scaling the values assigned to the ``Power Level'' control in the ``ZoneBaseboard:OutdoorTemperatureControlled'' EMS actuator.
