\section{Introduction}\label{introduction-001}

The ExpandObjects program uses HVACTemplate objects in the IDF file to ``expand'' them into full fledged objects for EnergyPlus. Read more details of the systems and the individual fields in the HVACTemplate objects in the Input Output Reference document.

ExpandObjects also processes GroundHeatTransfer objects, sends an input file to the Slab and Basement preprocessors, and replaces ground heat transfer boundary condition fields in building surface objects. Read more details of the ground heat transfer processing in the Input Output Reference.

Technically speaking, the ExpandObjects program is a preprocessor that is currently used with the HVACTemplate objects. The preprocessor reads an \textbf{idf} file and generates an expanded.idf file (usually with the extension .\textbf{expidf}). The original idf file contains objects that will be read by the preprocessor and those that are ignored by the preprocessor. The objects read can be either commented out or left as is. The objects created by the preprocessor in the expanded.idf file should require no further preprocessing. The preprocessor does not read the EnergyPlus Data Dictionary file (Energy+.IDD) and does limited validation. Most of the object values that are created are ``passed'' through from input objects. This allows EnergyPlus to provide most of the validation. If errors are found, error messages are passed to the EnergyPlus program using the Output:Preprocessor object. These errors will be shown in the usual EnergyPlus error file. When used with EP-Launch, the expanded.idf file is renamed to the original file name with the extension \textbf{expidf}.
