\section{pyExpandObjects}

\subsection{Introduction}\label{pyExpandObjects}

Much like the ExpandObjects program in Section 10.1, the pyExpandObjects expands HVACTemplate objects from an input epJSON file into an expanded file that can be directly run in EnergyPlus.  However, pyExpandObjects does not process GroundHeatTransfer objects or provide support for the Slab or Basement executables.

The pyExpandObjects program works as a preprocessor that maps HVACTemplate objects to regular objects in EnergyPlus.  This processor reads an epJSON file and generates and expanded epJSON file.  No further pre-processing should be required after the conversion has been performed.  Unlike ExpandObjects (10.1), a schema validation does occur when the file is read into the program, and error messages will be shown in the usual EnergyPlus error file.  By default, an invalid epJSON file will stop the program, but this requirement can be removed via command line options.  Please see the \href{https://epjson-expandobjects.readthedocs.io/en/latest/?badge=latest}{documentation} or '--help' command line option for further details.  Additionally, the default settings only produce an expanded file with an adjusted name ("<original-file-name>\_expanded.epJSON"). If the '--output-backups' option is used in the command line, then a file containing only the HVACTemplate objects ("<original-file-name>\_hvac\_templates.epJSON"), and a file containing all other objects ("<original-file-name>\_base.epJSON") will also be output.