\section{Example Error Messages for Preprocessors}\label{example-error-messages-for-preprocessors}

All of the preprocessing programs (e.g., EP-Macro, ExpandObjects) produce Output:PreprocessorMessage objects for the errors they detect. Any preprocessor can produce these objects.~ You may need to consult with actual preprocessor program documentation to understand these errors. The output preprocessor messages appear first in the .err file. The format for the messages are: \textless{}objectname\textgreater{} (i.e.~Output:Preprocessormessage) followed by the program name (e.g.~EPMacro) in quotes and then the strings for the message, whether Warning, Severe or Fatal.~ If Fatal, EnergyPlus will fatal out after producing all the error messages.

Here are some examples:

\subsection{Warning}\label{warning-000}

\begin{lstlisting}
Output:PreprocessorMessage = "EPXMLPreProc2" has the following Warning conditions:
   **   ~~~   ** Problem with the width for requested floor area and
   **   ~~~   ** perimeter depth.  Reduced perimeter depth from 4.57
   **   ~~~   ** to 3.656 to accommodate perimeter and core layout
\end{lstlisting}

\subsection{Severe}\label{severe-000}

\begin{lstlisting}
Output:PreprocessorMessage = "EPMacro" has the following Severe conditions:
   **   ~~~   ** at approximately input line number = 200: column = 11
   **   ~~~   ** cannot find/read include file
   **   ~~~   ** symbol = HVAC3ZoneMat-Const.imf
   **   ~~~   ** refer to <file>.epmdet for details.
\end{lstlisting}

Some preprocessor utility programs will give more details than others.~ Here, you see at input file line number 200, about column 11, that the program cannot find (or read) the include file and that there will be more details after the end of EnergyPlus processing in the file with epmdet for extension.

\begin{lstlisting}
Output:PreprocessorMessage = "GroundTempCalc - Slab" has the following Fatal condition:
   **   ~~~   ** No in.epw file found
\end{lstlisting}

This message is coming from the Slab preprocessor program after the ExpandObjects program has processed the input file and triggered the Slab program to be executed. There is no weather file and the Slab program cannot run.

\subsection{Fatal}\label{fatal-000}

Preprocessor condition(s) cause termination.

As you can see from the above Slab message, preprocessor programs may signal a fatal condition but the actual message you see in the .err file is a Severe. You will see the above message if any of the preprocessor conditions signaled a fatal error.
