\section{Example Error Messages during Sizing and Simulation}\label{example-error-messages-during-sizing-and-simulation}

\subsection{Warning}\label{warning}

\begin{lstlisting}
Calculated design cooling load for zone = B1AE_FCU02_AN is zero.
Check Sizing:Zone and ZoneControl:Thermostat inputs.
\end{lstlisting}

\begin{lstlisting}
Calculated design heating load for zone = B1AE\_FCU02\_AN is zero.
Check Sizing:Zone and ZoneControl:Thermostat inputs.
\end{lstlisting}

Two flavors of the same message showing up during Sizing. Read about Day Types in the Sizing:* objects.~ Schedules may affect how the program looks at loads during sizing. Another suggestion is:

Plot the zone temperature and check against the zone thermostat set point temperature.

\begin{lstlisting}
Output:Variable,*,Zone/Sys Air Temperature at Thermostat,timestep;
Output:Variable,*,Zone/Sys Thermostat Heating Setpoint,timestep;
\end{lstlisting}

If the zone temperature never falls below the thermostat set point temperature then there really is no load and lighting, equipment, occupancy, etc inputs/schedules need to be checked. Usually these types of load will be turned off for the design days in winter to correctly size the heating system. If the zone temperature does fall below the zone thermostat temperature, then the zone sizing objects probably have bad inputs.

\subsection{Severe}\label{severe}

\begin{lstlisting}
Temperature (high) out of bounds (206.82] for zone = "ZONE 1", for surface = "SOUTH WALL"
During Warmup & Sizing, Environment = ALEXANDRIA ESLER REGIONAL AP ANN HTG 99.6% CONDNS DB, at Simulation time = 12/21 01:00 - 01:04
Zone = "ZONE 1", Diagnostic Details:
...Internal Heat Gain [155.557] W/m2
...Infiltration/Ventilation [3.500E-002] m3/s
...Mixing/Cross Mixing [0.000] m3/s
...Zone is part of HVAC controlled system.
\end{lstlisting}

This error may be related to one of the warnings during get input routines on the Design Level of some heat gains at the zone level. Also to be noted here is the amount of Infiltration/Ventilation being introduced at the zone level. This diagnostics detail is produced once for each zone where the error occurs.

\subsection{Fatal}\label{fatal}

\begin{lstlisting}
EnergyPlus has exited due to the reason stated above
...Summary of Errors that led to program termination:
..... Reference severe error count = 11
..... Last severe error = Temperature (high) out of bounds (210.11] for zone = "ZONE 1", for surface = "ROOF1"
\end{lstlisting}

Typical fatal condition. A small summary of the number of severe errors that were produced along with the last severe error.
