\section{Line Trace}\label{line-trace}

You can use the EDD file to examine the execution of every line of code. If you request a verbose level of debugging output in the Output:EnergyManagementSystem input object, the EDD file will contain a series of text records that trace the execution of each line of Erl code. Traces contain the name of the program, the program line number, the text of the line, the result returned by executing the line (if any), and a timestamp that indicates when it was executed during the environment period. Note that the EDD file is only produced if you have EMS/Erl programs in your input file.

An example of a single trace follows. This is one record, or single line of text from one of the traces in an EDD file.

\begin{lstlisting}
VAV1MIXEDAIRMANAGERS,Line 1,SET VAV_1_COOLC_SETPOINT = SEASONAL_RESET_SAT_SCHED - ( T_VAV1FANOUT - T_VAV1FANIN),13.0000000000000, During Warmup, Occurrence info = CHICAGO IL USA TMY2-94846 WMO\# = 725300, 01/01 18:30 - 18:45
\end{lstlisting}

Each block of text is separated by comma, so the trace information could be read into a spreadsheet and formatted to columns using comma separation.

``VAV1MIXEDAIRMANAGERS'' is the name of a user-defined Erl Program.

``Line 1'' indicates that this trace is from the first line of the Erl program called VAV1MIXEDAIRMANAGERS.

The next block of text, ``SET VAV\_1\_COOLC\_SETPOINT = SEASONAL\_RESET\_SAT\_SCHED - ( T\_VAV1FANOUT - T\_VAV1FANIN)'' is the Erl program statement contained at Line 1 in the Erl program called VAV1MIXEDAIRMANAGERS.

The value ``13.0000000000000'' is the result of this particular SET statement. The value of 13.0 has been assigned to the variable called VAV\_1\_COOLC\_SETPOINT.

The next block of text ``During Warmup'' indicates that the line was executed while the simulation was in a warm up phase. (Warmup happens during the beginning of each environment period to precondition the model's transients with the conditions of the first day.)

The next block of text ``Occurrence info = CHICAGO IL USA TMY2-94846 WMO\# = 725300'' indicates the environment period being simulated. This is a weather-file-based RunPeriod for Chicago using TMY2 data source associated with weather station number 725300.

The last block of text ``01/01 18:30 - 18:45'' is the date and time of day for the simulation timestep when the Erl program line was executed.
