\section{Running EnergyPlus by Hand}\label{running-energyplus-by-hand}

EnergyPlus runs as a console application with optional command line arguments. The arguments may be listed by typing \lstinline!energyplus --help! (on any operating system) and \lstinline!man energyplus! (on Unix-based operating systems, Mac OS X and Linux). For more information about the command line interface, see \url{https://github.com/NREL/EnergyPlus/blob/develop/doc/running-energyplus-from-command-line.md}. The remainder of this section describes running EnergyPlus in legacy mode (i.e.~no command-line arguments) on Windows OS.

To run the program bring up the command prompt and ``cd'' to the directory containing the executable. Assume that the executable is called \emph{EnergyPlus.exe}. In the same directory EnergyPlus expects \emph{in.idf}, the input data file; \emph{Energy+.idd}, the data dictionary file; \emph{in.epw}, the weather file (needed only if there is a RunPeriod in the input); and optionally \emph{Energy+.ini}, the initialization file. Typing ``EnergyPlus'' (and hitting the \emph{Enter} key) will execute the program. EnergyPlus will write messages to the command window as it runs. A simulation with two design days and one run period looks like:

\begin{lstlisting}
 EnergyPlus Starting
 EnergyPlus, Version 1.3
 Warming up
 Initializing Response Factors
 Calculating CTFs for "EXTWALL80", Construction \#1
 Calculating CTFs for "PARTITION06", Construction \#2
 Calculating CTFs for "FLOOR SLAB 8 IN", Construction \#3
 Calculating CTFs for "ROOF34", Construction \#4
 Initializing Window Optical Properties
 Initializing Solar Calculations
 Initializing HVAC
 Warming up
 Warming up
 Warming up
 Performing Zone Sizing Simulation
 Warming up
 Warming up
 Warming up
 Performing Zone Sizing Simulation
 Initializing New Environment Parameters
 Warming up {1}
 Warming up {2}
 Warming up {3}
 Warming up {4}
 Starting Simulation at 01/14 for CHICAGO IL UNITED STATES TMY2 94846 WMO# = 725340
 Initializing New Environment Parameters
 Warming up {1}
 Warming up {2}
 Warming up {3}
 Warming up {4}
 Starting Simulation at 07/07 for CHICAGO IL UNITED STATES TMY2 94846 WMO# = 725340
 EnergyPlus Run Time = 00hr 00min  7.31sec
\end{lstlisting}

When execution is finished, \emph{eplusout.err} and \emph{eplusout.audit} will always appear. If the program terminated with an input error, these may be the only output files. If the program runs normally, \emph{eplusout.eio} will appear. Depending on what was requested in the input, the other output files described above will also be written.
