\section{CoeffConv}\label{coeffconv}

CoeffConv is a program to convert DOE-2 temperature dependent curves in Fahrenheit to EnergyPlus curves in Centigrade. The program converts the DOE-2 coefficients of a biquadratic curve to the equivalent EnergyPlus biquadratic curve coefficients.

EP-Launch can be used to run the CoeffConv program. CoeffConv is one of the options on the Utilities tab in EP-Launch. See the EP-Launch section in this document for more information on how to use EP-Launch with the CoeffConv program. When using EP-Launch to run CoeffConv the input file must have the file extension .coi and will create an output file with the file extension .coo.

You can also run the CoeffConv program as a console application. The input file then must be from file CoeffConvInput.txt (status = OLD). There are 6 lines of ascii input.

For example:

\begin{lstlisting}
VarSpeedCoolCapFt
-0.29382,0.0222213,0.00006988,0.0040928,-0.00000226,-0.00013774
55.,75.
75.,115.
67.0,95.0
5.0
\end{lstlisting}

\begin{itemize}
\tightlist
\item
  The 1st line is the user selected name of the curve.
\item
  The 2nd line contains the 6 biquadratic curve coefficients, comma separated. These are the Doe-2 coefficients.
\item
  The 3rd line contains the min and max values of the 1st independent variable, comma separated, deg F.
\item
  The 4th line contains the min and max values of the 2nd independent variable, comma separated, deg F.
\item
  The 5th line contains the rated values of the 1st \& 2nd independent variables, comma separated, deg F.
\item
  The 6th line contains the delta T for the output performance maps.
\end{itemize}

All the input lines should start in column 1.

The above sequence can be repeated up to 100 times.

The output file is CoeffConvOutput.txt (status = NEW) (that means you need to delete any existing CoeffConvOutput.txt).

The output file will contain the EnergyPlus idf input for the curve, as well as any error messages;

Also, the DOE-2 and EnergyPlus curve values at the rating point (where the value should be 1.0) and performance maps for the curves - both DOE-2 and EnergyPlus.

There is an example input file and an example output file installed with the program.
