\section{Outdoor Air System}\label{outdoor-air-system}

The AirLoopHVAC:OutdoorAirSystem is a subsystem of the primary air system (object AirLoopHVAC). To the primary air system it appears to be a single component. Within the subsystem are components and controllers very much like the primary air system. The purpose of the outside air system is to simulate the splitting of the return air into relief and recirculated air; mix the recirculated and outside air to obtain the mixed air (all accomplished by the OutdoorAir:Mixer); simulate the components in the outside air stream; control the components and outside air flow rate (economizer control). The outside air system differs from the primary air system in that it is not described in terms of splitters, mixers, and branches. Instead the components are simply listed in simulation order in an AirLoopHVAC:OutdoorAirSystem:EquipmentList input object. The components other than the OutdoorAir:Mixer are assumed to be in the outside air stream. The connectivity is defined by upstream component's outlet node = downstream component's inlet node. The OutdoorAir:Mixer should be the first component in the AirLoopHVAC:OutdoorAirSystem:EquipmentList object.

\subsection{Simulation}\label{simulation-002}

The data for and simulation of the outside air system are contained in the MixedAir module. This includes the data and simulation of the OutdoorAir:Mixer and the Controller:OutdoorAir. The simulation of the outside air system is straightforward.

\begin{itemize}
\item
  All controllers other than Controller:OutdoorAir are moved up to the primary air system level, where they are simulated with the primary air system controllers.
\item
  The Controller:OutdoorAir is simulated.
\item
  The components contained in the outside air system are simulated in the order of their input in the AirLoopHVAC:OutdoorAirSystem:EquipmentList.
\end{itemize}
