\section{Internal Gains and Exterior Lights}\label{internal-gains-and-exterior-lights}

\subsection{People}\label{people}

An actuator called ``People'' is available with a control type called ``Number of People.''~ This allows you to dictate the number of people in a zone. The units are persons. The unique identifier is the name of the people input object. Because you cannot really control people, this is an example the EMS in EnergyPlus departing from the real world of building EMS.

\subsection{Lights}\label{lights}

An actuator called ``Lights'' is available with a control type called ``Electricity Rate'' (in W)~ This allows you to set the lighting power associated with each Lights input object. The unique identifier is the name of the Lights input object.

\subsection{Electric Equipment}\label{electric-equipment}

An actuator called ``ElectricEquipment'' is available with a control type called ``Electricity Rate'' (in W). This allows you to set the power associated with each ElectricEquipment input object. The unique identifier is the name of the ElectricEquipment input object.

\subsection{Gas Equipment}\label{gas-equipment}

An actuator called ``GasEquipment'' is available with a control type called ``NaturalGas Rate'' (in W). This allows you to set the power associated with each GasEquipment input object.~ The unique identifier is the name of the GasEquipment input object.

\subsection{Hot Water Equipment}\label{hot-water-equipment}

An actuator called ``HotWaterEquipment'' is available with a control type called ``District Heating Power Level'' (in W). This allows you to set the power associated with each HotWaterEquipment input object. The unique identifier is the name of the HotWaterEquipment input object.

\subsection{Steam Equipment}\label{steam-equipment}

An actuator called ``SteamEquipment'' is available with a control type called ``District Heating Power Level'' (in W). This allows you to set the power associated with each SteamEquipment input object. The unique identifier is the name of the SteamEquipment input object.

\subsection{Other Equipment}\label{other-equipment}

An actuator called ``OtherEquipment'' is available with a control type called ``Power Level'' (in W). This allows you to set the power associated with each OtherEquipment input object. The unique identifier is the name of the OtherEquipment input object.

Other equipment offers a way to adjust the zone air energy balance without consuming any energy resources.

\subsection{Baseboard}\label{baseboard}

An actuator called ``ZoneBaseboard:OutdoorTemperatureControlled'' is available with a control type called ``Power Level'' (in W). The unique identifier is the name of the ZoneBaseboard:OutdoorTemperatureControlled input object.

\subsection{Exterior Lights}\label{exterior-lights}

An actuator called ``ExteriorLights'' is available with a control type called ``Electricity Rate'' (in W). The unique identifier is the name of the Exterior:Lights input object.
