\section{Thermal Envelope}\label{thermal-envelope}

\subsection{Window Shading Control}\label{window-shading-control}

Actuators called ``Window Shading Control'' are available with actuated component control type called ``Control Status'' in [ShadeStatus] and ``Slat Angle'' in [degree]. This actuator is available in models that also have the WindowShadingControl input objects. The user-defined name for the WindowShadingControl is not used to identify unique window shading controls; rather, the window name is used to identify the actuator. This is because there could be multiple windows, all with shades, each of which is governed by a single WindowShadingControl input object. The EMS actuator can override the control actions for each window separately.

The control is actuated by setting values for the control status. The settings are numeric but represent discrete states the control can take. The appropriate values depend on the type and position of the shading device. There are three basic types of shading devices:~ switchable glazings, shades, and blinds. (Shades are described with WindowMaterial:Shade input objects. Blinds are described with WindowMaterial:Blind input objects.)~ Shades and blinds can be situated in the exterior, between the glass, or in the interior.

The following settings are valid and must be used:

\begin{itemize}
\item
  --1.0: ~~~ No shading device.
\item
  0.0: ~~~~~ Shading device is off (applies to shades and blinds).
\item
  1.0: ~~~~~ Interior shade is on.
\item
  2.0:~~~~~~ Glazing is switched to a darker state (switchable glazings only).
\item
  3.0: ~~~~~ Exterior shade is on.
\item
  6.0: ~~~~~ Interior blind is on.
\item
  7.0: ~~~~~ Exterior blind is on.
\item
  8.0: ~~~~~ Between-glass shade is on.
\item
  9.0: ~~~~~ Between-glass blind is on.
\end{itemize}

\subsection{Slat Angle}\label{slat-angle}

If the shading device is a blind, there is also a control type called ``Slat Angle.''~ This angle control is a continuous numeric value from 0.0 to 180.0. The angle is defined as between the glazing system's outward normal and the slat's outward normal (see the diagram in the input output reference under WindowMaterial:Blind).

\subsection{Surface Convection Heat Transfer Coefficient}\label{surface-convection-heat-transfer-coefficient}

Two actuators called ``Surface'' are available with the control types of ``Interior Surface Convection Heat Transfer Coefficient'' and ``Exterior Surface Convection Heat Transfer Coefficient.''~ These provide direct control over the convection coefficient. The units are W/m\(^{2}\)-K. The unique identifier is the surface name.

This actuator controls the heat transfer modeling. Changes in air distribution systems can affect the interior surface convection coefficients. A sheltered exterior surface may have a lower surface heat transfer coefficient. This actuator provides a method of applying new models for convection coefficients.

\subsection{Material Surface Properties}\label{material-surface-properties}

Three actuators are available for controlling the surface properties material related to absorptance. Those material layers used in a Construction object that lie at the outside and the inside of the assembly determine the surface properties of a heat transfer surface.~ Actuators called ``Material'' are available with the control types ``Surface Property Solar Absorptance,'' ``Surface Property Thermal Absorptance,'' and ``Surface Property Visible Absorptance.''~ These are dimensionless parameters between 0.0 and 1.0.~ These actuators are useful for modeling switchable coatings such as thermochromic paints.

\subsection{Surface Construction State}\label{surface-construction-state}

An actuator is available for controlling the construction assigned to a surface that can be useful for modeling dynamic technologies for thermal envelopes.~ These actuators are called ``Surface'' and have a control type ``Construction State.''~ This actuator is used in conjunction with the input object called EnergyManagementSystem:ConstructionIndexVariable.~ Each Construction object defined in an input file has an index that points to where the data for that construction are stored in the program's internal data structures.~ The EnergyManagementSystem:ConstructionIndexVariable input object is used to create and fill a global Erl variable with the value that points to the specific construction named in the object. The Erl variable is what you assign to the construction state actuator's variable to override the construction assigned to a particular surface.~ When the actuator is set to Null, the surface reverts to the Construction originally referenced by the surface in the input file.

When using surface construction state to change window properties in combination with daylighting calculations, then the Calculation Method in the ShadowCalculation object must be set to TimestepFrequency. This will cause the daylighting factor calculations to be updated every timestep.

Using the surface construction state actuator brings with it a high degree of risk when it comes to modeling thermal heat capacity and transient heat transfer in opaque surfaces.~ If this actuator is used inappropriately, for example to assign different constructions, to a single surface, that have radically different heat storage capacities, then the heat transfer modeling results may not be physically accurate.~ When a construction state is overridden using this actuator, the thermal history data that evolved while using the previous construction are reused for the new construction. When this actuator is used, the program attempts to detect if incompatible constructions are being assigned. In some cases it issues a warning and allows the assignments to proceed, in others it warns and doesn't allow the assignment to proceed.~ If the original construction assigned to a surface has internal source/sink (defined using Construction:InternalSource) then any assignments to the surface must also be internal source constructions.~ If using the heat transfer algorithm called ConductionFiniteDifference, then the constructions must have the same number of finite difference nodes or the assignment is not allowed.~ The construction state actuator cannot be used in conjunction with the heat transfer algorithms called ConductionFiniteDifferenceSimplified or CombinedHeatAndMoistureFiniteElement.

\subsection{Surface Boundary Conditions}\label{surface-boundary-conditions}

Four actuators, called ``Other Side Boundary Conditions,'' are available for controlling the convection and radiation boundary conditions for surfaces that use ``OtherSideConditionsModel.''~ Each instance of a SurfaceProperty:OtherSideConditionsModel object will make available these actuators with the following four control types:

\begin{itemize}
\item
  ``Convection Bulk Air Temperature.''~ This is the temperature of the ambient air exposed to the surface, in degrees C.~ This is the temperature used for surface convection heat transfer boundary conditions on the outdoor, outside-face, other side of the surface.
\item
  ``Convection Heat Transfer Coefficient.''~ This is the heat transfer coefficient, in W/(m-K) used for surface convection boundary conditions on the outdoor, outside-face, or other side of the surface.
\item
  ``Radiation Effective Temperature.''~ This is the effective temperature of the environment surrounding the surface, in degrees C.~ This is the temperature used for surface thermal radiation heat transfer boundary conditions on the outdoor, outside-face, other side of the surface.
\item
  ``Radiation Linear Heat Transfer Coefficient.''~ This is the linearized heat transfer coefficient, in W/(m-K), used for surface thermal radiation boundary conditions on the outdoor, outside-face, or other side of the surface.
\end{itemize}

When using these actuators, values should be set for all four types.~ This boundary condition has no solar, only convection and radiation.
