\input{../title}

\chapter{Auxiliary Programs Introduction}\label{auxiliary-programs-introduction}

This document will describe several of the ``auxiliary programs'' of the EnergyPlus system in more detail. Some of these programs are only available or only distributed for certain platforms. Typically, the programs are available on the Windows platform. Within the descriptions, other platforms will be noted as applicable. These programs include:

\textbf{Weather Converter Program} (aka ``Weather'')

\textbf{Ground Heat Transfer in EnergyPlus} - Procedure for Ground Temperature creation

\textbf{View Factor Calculation Program} - Auxiliary program used to calculate View Factors which can be used with EnergyPlus

\textbf{Using Older Version Input Files - Transition} - to convert input files from one version to another upon release of a new version

\textbf{EPDraw} - Create DXF files from your input files

\textbf{Input Macros} - Use a macro language to increase efficiency in creating EnergyPlus input files. Unfortunately, IDF files containing macros cannot be read in the IDF Editor.

\textbf{HVAC Diagram} - Use a post processing program to diagram your HVAC inputs.

\textbf{CoeffConv/CoeffCheck} - Convert DOE-2 temperature dependent curves (Fahrenheit) to EnergyPlus temperature curves (Centigrade/Celsius)

\textbf{ExpandObjects} - Some technical details of the Expand Objects program which preprocessed HVACTemplate:* and GroundHeatTransfer:* objects for use inside EnergyPlus.

\textbf{CSVproc} - Get simple statistics from CSV output files.

\textbf{convertESOMTR} - convert your outputs to Inch-Pound (default) or other custom unit conversions.

\textbf{CalcSoilSurfTemp Program} - calculate soil surface parameters used in the Earth Tube simulation

\textbf{HVAC Performance Curve Fit Tool}- generates HVAC performance curves in EnergyPlus IDF format

\textbf{Parametric Spreadsheets} - Parametric spreadsheets are available to help illustrate or calculate some parameters/coefficients.

\textbf{ParametricPreprocessor} \textbf{-} Special objects can be inserted in IDF files and generate a series of IDF files from a single source IDF file that contains parametric objects and expressions. Unlike using the macro language, these input files are capable of being read in the IDF Editor.

\textbf{AppGPostProcess - Appendix G PostProcessing program} - The ASHRAE 90.1 Appendix G postprocessing program takes simulation outputs and processes them to help meet Appendix G requirements..

\textbf{BLASTTranslator} - The BLAST translator can take BLAST (Building Loads Analysis and System Thermodynamics) input files and make them ready for running in EnergyPlus.

\textbf{DOE2Translator} - The DOE-2 translator can take DOE-2 program input files and make them ready for running in EnergyPlus.

\textbf{Running Console Applications} - this section describes how to run console applications that are part of EnergyPlus and how you might modify these to your specific needs. Instructions for running individual programs are included in their descriptions.

\textbf{Technical Details of Running EnergyPlus} - this section gives full instructions on both EP-Launch and the IDF-Editor as well as some more details on running EnergyPlus manually.

\textbf{EP-Compare} - A utility to graphically compare tabular results from multiple simulation files.
