\section{Adding new features}\label{adding-new-features}

The process for adding new features or significantly changing some features goes through a development team discussion period where the new feature is outlined, discussed and (hopefully) approved for inclusion.

The team has a New Feature Proposal template document that is available to anyone wishing to add a new feature to EnergyPlus (or to auxiliary programs around EnergyPlus). The full New Feature Proposal format is shown in Appendix F.

The sections of the New Feature Proposal are summarized in the following table:

% table 1
\begin{longtable}[c]{p{1.5in}p{4.5in}}
\caption{Sections of a New Feature Proposal \label{table:sections-of-a-new-feature-proposal}} \tabularnewline
\toprule 
Section & Description \tabularnewline
\midrule
\endfirsthead

\caption[]{Sections of a New Feature Proposal} \tabularnewline
\toprule 
Section & Description \tabularnewline
\midrule
\endhead

Justification & Why is the feature important.~ Impact on energy use. What energy aspects the feature is using. \tabularnewline
Conference Call Conclusions & Conclusions from the discussions (email or conference call) \tabularnewline
Other Conference Call topics & Items outside the scope of the feature might be brought up but not able to be accomplished. \tabularnewline
Overview & Description of the feature and references \tabularnewline
Approach & What approach will be used. \tabularnewline
Testing/Validation data Sources & Required \tabularnewline
IORef/Draft & IDD Objects (new or revised) as well as full IOReference text \tabularnewline
Proposed Report Variables & What outputs will come out of this feature. \tabularnewline
Proposed additions to meters & How the outputs will affect the meter output \tabularnewline
Engineering Reference Draft & Draft text for the Engineering Reference document \tabularnewline
Example File & What/how many example files will be included or used to support this feature \tabularnewline
Transition changes & What will be the required changes for current input files for this feature \tabularnewline
Other documents & Other references. \tabularnewline
\bottomrule
\end{longtable}

Then, of course, the document in Appendix G must be filled out and given to the proper people as well -- to show that rights to the intellectual property of the new feature are owned by the developer.
