\section{Transition Console Program Details}\label{transition-console-program-details}

For those who are interested, this is the detailed description of the Transition console applications including the current one. There are methods to use the program set from the command line; those details are not included in this document but available from EnergyPlus Support group.

TransitionVA-B-C-to-VD-E-F.exe is the transition program that converts files from version ``A-B-C'' to ``D-E-F'', and is distributed in the ``D-E-F'' installer package. It uses several important files that are included in the ``EnergyPlus'' installation folder, in the PreProcess/IDFVersionUpdator subdirectory.

% table 28
\begin{longtable}[c]{p{2.14in}p{3.85in}}
\caption{Transition files for current release \label{table:transition-files-for-current-release}} \tabularnewline
\toprule 
File Name & Description \tabularnewline
\midrule
\endfirsthead

\caption[]{Transition files for current release} \tabularnewline
\toprule 
File Name & Description \tabularnewline
\midrule
\endhead

TransitionVA-B-C-to-VD-E-F.exe & The executable program \tabularnewline
VA-B-C-Energy+.idd & Base, starting, version Energy+.idd file \tabularnewline
VD-E-F-Energy+.idd & Target, new idd file; Identical to Energy+.idd when distributed \tabularnewline
Report Variables A-B-C to D-E-F.csv & Report variable name changes \tabularnewline
\bottomrule
\end{longtable}

Another file ``RulesA-B-C-to-D-E-F.xls'' is not used directly by the program but contains the ``rules'' for translating objects from version A-B-C release to the D-E-F release. The ObjectStatus file can also be viewed - it will show if deleted objects are automatically transitioned to the new input file versions.

There are several methods to executing the transition program - these methods give you the most flexibility in changing files from one version to the next. The easiest transition is through the EP-Launch program which can detect if the input file about to be run is of the same version as the IDD or not and suggest transitioning. You can also manually transition from the file menu in EP-Launch. (To have this feature, you must also have the files from the preceding table in the same folder as EP-Launch - which is usually the folder that also has the EnergyPlus.exe program).

There are two command line methods to execute the transition version (from the Command Prompt). One is to simply use the file name you want transitioned (including .rvi or .mvi file names) or you can use a file name with a .lst extension and simply enter file names to be done in a text file. When you execute the transition program in this fashion, you will get the ``typical'' program defaults of a ``full'' transition, field names will be shown at each field with units, and any blank fields will be left blank rather than filled in with the current defaults.
