\section{Other Software included or referenced directly}\label{other-software-included-or-referenced-directly}

The following notices apply to those EnergyPlus distributions which include the interface to BCVTB or Functional Mock-up Units.

\subsection{ZLIB DATA COMPRESSION LIBRARY}\label{zlib-data-compression-library}

zlib 1.2.5 is a general purpose data compression library.~ All the code is thread safe.~ The data format used by the zlib library is described by RFCs (Request for Comments) 1950 to 1952 in the files \url{http://www.ietf.org/rfc/rfc1950.txt} (zlib format), rfc1951.txt (deflate format) and rfc1952.txt (gzip format).

All functions of the compression library are documented in the file zlib.h (volunteer to write man pages welcome, contact zlib@gzip.org).~ A usage example of the library is given in the file example.c which also tests that the library is working correctly. ~Another example is given in the file minigzip.c.~ The compression library itself is composed of all source files except example.c and minigzip.c.

To compile all files and run the test program, follow the instructions given at the top of Makefile.in.~ In short ``./configure; make test'', and if that goes well, ``make install'' should work for most flavors of Unix.~ For Windows, use one of the special makefiles in win32/ or contrib/vstudio/ .~ For VMS, use make\_vms.com.~ Questions about zlib should be sent to \textless{}zlib@gzip.org\textgreater{}, or to Gilles Vollant \textless{}info@winimage.com\textgreater{} for the Windows DLL version.~ The zlib home page is \url{http://zlib.net/} .~ Before reporting a problem, please check this site to verify that you have the latest version of zlib; otherwise get the latest version and check whether the problem still exists or not.

PLEASE read the zlib FAQ \url{http://zlib.net/zlib_faq.html} before asking for help.

Mark Nelson \textless{}markn@ieee.org\textgreater{} wrote an article about zlib for the Jan.~ 1997 issue of Dr.~ Dobb's Journal; a copy of the article is available online\footnote{\url{http://marknelson.us/1997/01/01/zlib-engine/}}.

The changes made in version 1.2.5 are documented in the file ChangeLog.

Unsupported third party contributions are provided in directory contrib/ .

zlib is available in Java using the java.util.zip package, documented online\footnote{\url{http://java.sun.com/developer/technicalArticles/Programming/compression/}}.

A Perl interface to zlib written by Paul Marquess \textless{}pmqs@cpan.org\textgreater{} is available at CPAN (Comprehensive Perl Archive Network) sites, including \url{http://search.cpan.org/pmqs/IO-Compress-Zlib/}.

A Python interface to zlib written by A.M. Kuchling \textless{}amk@amk.ca\textgreater{} is available in Python 1.5 and later versions, see \url{http://www.python.org/doc/lib/module-zlib.html}.

zlib is built into tcl: \url{http://wiki.tcl.tk/4610} .

An experimental package to read and write files in .zip format, written on top of zlib by Gilles Vollant \textless{}info@winimage.com\textgreater{}, is available in the contrib/minizip directory of zlib.

Notes for some targets:

\begin{itemize}
\item
  For Windows DLL versions, please see win32/DLL\_FAQ.txt
\item
  For 64-bit Irix, deflate.c must be compiled without any optimization. With -O, one libpng test fails. The test works in 32 bit mode (with the -n32~~ compiler flag). The compiler bug has been reported to SGI.
\item
  zlib doesn't work with gcc 2.6.3 on a DEC 3000/300LX under OSF/1 2.1 it works when compiled with cc.
\item
  On Digital Unix 4.0D (formely OSF/1) on AlphaServer, the cc option -std1 is necessary to get gzprintf working correctly. This is done by configure.
\item
  zlib doesn't work on HP-UX 9.05 with some versions of /bin/cc. It works with other compilers. Use ``make test'' to check your compiler.
\item
  gzdopen is not supported on RISCOS or BEOS.
\item
  For PalmOs, see \url{http://palmzlib.sourceforge.net/}
\end{itemize}

Acknowledgments:

~ The deflate format used by zlib was defined by Phil Katz.~ The deflate and zlib specifications were written by L.~ Peter Deutsch.~ Thanks to all the people who reported problems and suggested various improvements in zlib; they are too numerous to cite here.

Copyright notice:

~(C) 1995-2010 Jean-loup Gailly and Mark Adler

This software is provided `as-is', without any express or implied warranty.~ In no event will the authors be held liable for any damages arising from the use of this software.

Permission is granted to anyone to use this software for any purpose, including commercial applications, and to alter it and redistribute it freely, subject to the following restrictions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The origin of this software must not be misrepresented; you must not claim that you wrote the original software. If you use this software in a product, an acknowledgment in the product documentation would be appreciated but is not required.
\item
  Altered source versions must be plainly marked as such, and must not be misrepresented as being the original software.
\item
  This notice may not be removed or altered from any source distribution.
\end{enumerate}

~ Jean-loup Gailly~~~~~~~ Mark Adler

~ jloup@gzip.org~~~~~~~~~ madler@alumni.caltech.edu

~

If you use the zlib library in a product, we would appreciate *not* receiving lengthy legal documents to sign.~ The sources are provided for free but without warranty of any kind.~ The library has been entirely written by Jean-loup Gailly and Mark Adler; it does not include third-party code.

If you redistribute modified sources, we would appreciate that you include in the file ChangeLog history information documenting your changes.~ Please read the FAQ for more information on the distribution of modified source versions.

\subsection{ExPat Copying Notice}\label{expat-copying-notice}

Copyright (c) 1998, 1999, 2000 Thai Open Source Software Center Ltd

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the ``Software''), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED ``AS IS'', WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

\subsection{FMU SDK license}\label{fmu-sdk-license}

Copyright (c) 2008-2011, QTronic GmbH. All rights reserved.

The FmuSdk is licensed by the copyright holder under the BSD License\footnote{\url{http://www.opensource.org/licenses/bsd-license.html}}: Redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met:

\begin{itemize}
\item
  Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.
\item
  Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.
\end{itemize}

THIS SOFTWARE IS PROVIDED BY QTRONIC GMBH ``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL QTRONIC GMBH BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\subsection{Minizip Notice}\label{minizip-notice}

Condition of use and distribution are the same than zlib :

This software is provided `as-is', without any express or implied warranty.~ In no event will the authors be held liable for any damages arising from the use of this software.

Permission is granted to anyone to use this software for any purpose, including commercial applications, and to alter it and redistribute it freely, subject to the following restrictions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The origin of this software must not be misrepresented; you must not claim that you wrote the original software. If you use this software in a product, an acknowledgment in the product documentation would be appreciated but is not required.
\item
  Altered source versions must be plainly marked as such, and must not be misrepresented as being the original software.
\item
  This notice may not be removed or altered from any source distribution.
\end{enumerate}

\subsection{MODELISAR Notice}\label{modelisar-notice}

Copyright (c) 2008-2010, MODELISAR consortium. All rights reserved.

This file is licensed by the copyright holders under the BSD License\footnote{\url{http://www.opensource.org/licenses/bsd-license.html\textgreater}}:

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Redistribution and use in source and binary forms, with or withoutmodification, are permitted provided that the following conditions are met:

\begin{itemize}
\item
  Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.
\item
  Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.
\item
  Neither the name of the copyright holders nor the names of its contributors may be used to endorse or promote products derived from this software without specific prior written permission.
\end{itemize}

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS ``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\subsection{Functional Mock-up Unit for Co-Simulation Import Notice}\label{functional-mock-up-unit-for-co-simulation-import-notice}

Functional Mock-up Unit for Co-Simulation Import in EnergyPlus Copyright (c) 2012, The Regents of the University of California, through Lawrence Berkeley National Laboratory (subject to receipt of any required approvals from the U.S. Dept. of Energy). All rights reserved.

If you have questions about your rights to use or distribute this software, please contact Berkeley Lab's Technology Transfer Department at \textless{}TTD@lbl.gov\textgreater{}.

NOTICE.~ This software was developed under partial funding from the U.S. Department of Energy.~ As such, the U.S. Government has been granted for itself and others acting on its behalf a paid-up, nonexclusive, irrevocable, worldwide license in the Software to reproduce, prepare derivative works, and perform publicly and display publicly.~ Beginning five (5) years after the date permission to assert copyright is obtained from the U.S. Department of Energy, and subject to any subsequent five (5) year renewals, the U.S. Government is granted for itself and others acting on its behalf a paid-up, nonexclusive, irrevocable, worldwide license in the Software to reproduce, prepare derivative works, distribute copies to the public, perform publicly and display publicly, and to permit others to do so.

Modified BSD License agreement

Functional Mock-up Unit for Co-Simulation Import in EnergyPlus Copyright (c) 2012, The Regents of the University of California, through Lawrence Berkeley National Laboratory (subject to receipt of any required approvals from the U.S. Dept. of Energy).~ All rights reserved.

Redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met:

Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.

Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.

Neither the name of the University of California, Lawrence Berkeley National Laboratory, U.S. Dept. of Energy nor the names of its contributors may be used to endorse or promote products derived from this software without specific prior written permission.

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS ``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

You are under no obligation whatsoever to provide any bug fixes, patches, or upgrades to the features, functionality or performance of the source code (``Enhancements'') to anyone; however, if you choose to make your Enhancements available either publicly, or directly to Lawrence Berkeley National Laboratory, without imposing a separate written license agreement for such Enhancements, then you hereby grant the following license: a non-exclusive, royalty-free perpetual license to install, use, modify, prepare derivative works, incorporate into other computer software, distribute, and sublicense such enhancements or derivative works thereof, in binary and source code form.

\subsection{Functional Mock-up Unit Export of EnergyPlus Notice}\label{functional-mock-up-unit-export-of-energyplus-notice}

Functional Mock-up Unit Export of EnergyPlus (c)2013, The Regents of the University of California, through Lawrence Berkeley National Laboratory (subject to receipt of any required approvals from the U.S. Department of Energy). All rights reserved.

If you have questions about your rights to use or distribute this software, please contact Berkeley Lab's Technology Transfer Department at \textless{}TTD@lbl.gov\textgreater{}.referring to ``Functional Mock-up Unit Export of EnergyPlus (LBNL Ref 2013-088)''.

NOTICE: This software was produced by The Regents of the University of California under Contract No. DE-AC02-05CH11231 with the Department of Energy.

For 5 years from November 1, 2012, the Government is granted for itself and others acting on its behalf a nonexclusive, paid-up, irrevocable worldwide license in this data to reproduce, prepare derivative works, and perform publicly and display publicly, by or on behalf of the Government. There is provision for the possible extension of the term of this license.

Subsequent to that period or any extension granted, the Government is granted for itself and others acting on its behalf a nonexclusive, paid-up, irrevocable worldwide license in this data to reproduce, prepare derivative works, distribute copies to the public, perform publicly and display publicly, and to permit others to do so. The specific term of the license can be identified by inquiry made to Lawrence Berkeley National Laboratory or DOE. Neither the United States nor the United States Department of Energy, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any data, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.

Copyright (c) 2013, The Regents of the University of California, Department of Energy contract-operators of the Lawrence Berkeley National Laboratory.

All rights reserved.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met: 
\end{enumerate}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  Redistributions of source code must retain the copyright notice, this list of conditions and the following disclaimer.
\item
  Redistributions in binary form must reproduce the copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.
\item
  Neither the name of the University of California, Lawrence Berkeley National Laboratory, U.S. Dept. of Energy nor the names of its contributors may be used to endorse or promote products derived from this software without specific prior written permission. 
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS ``AS IS''
\end{enumerate}

AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  You are under no obligation whatsoever to provide any bug fixes, patches, or upgrades to the features, functionality or performance of the source code (``Enhancements'') to anyone; however, if you choose to make your Enhancements available either publicly, or directly to Lawrence Berkeley National Laboratory, without imposing a separate written license agreement for such Enhancements, then you hereby grant the following license: a non-exclusive, royalty-free perpetual license to install, use, modify, prepare derivative works, incorporate into other computer software, distribute, and sublicense such enhancements or derivative works thereof, in binary and source code form.
\end{enumerate}

NOTE: This license corresponds to the ``revised BSD'' or ``3-clause BSD''

License and includes the following modification: Paragraph 3. has been added.

\subsection{Kiva License}\label{kiva-license}

Copyright (c) 2012-2018 Big Ladder Software LLC. All rights reserved.

Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the following conditions are met:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
Redistributions of source code must retain the above copyright notice, this
list of conditions and the following disclaimer.
\item
Redistributions in binary form must reproduce the above copyright notice,
this list of conditions and the following disclaimer in the documentation
and/or other materials provided with the distribution.
\item
Neither the name of the copyright holder nor the names of its contributors
may be used to endorse or promote products derived from this software without
specific prior written permission from the copyright holders.
\end{enumerate}

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDER AND CONTRIBUTORS "AS IS"
AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
